% ----------------------------------------------------------
% Merative
% ----------------------------------------------------------
% 		Data Scientist
\newcommand\merativeDescription{Technical lead on the delivery of large \& complex AI and Cognitive led transformation programs and works with Merative \& Partners to optimize tools and delivery methods.}

% ----------------------------------------------------------
% IBM
% ----------------------------------------------------------
% 		Advisory Data Scientist
\newcommand\ibmAdsDescription{Technical lead on delivery of Cognitive \& AI led programs using diverse data sources, such as electronic health record data, insurance claims data, scheduling and financial data, social determinants of health data, and any other relevant sources.}

% ----------------------------------------------------------
% 		Senior Data Curation Architect
\newcommand\ibmSdcaDescription{Senior member of Data Onboarding \& Governance for integration of healthcare data and enrichment of metadata. Configuration of data models, analytics, reports, and visualizations.}

% ----------------------------------------------------------
% 		Data Curation Architect
\newcommand\ibmDcaDescription{Lead member of Data Onboarding \& Governance, member of the Watson Foundation for Health Solutions Architecture team.}

% ----------------------------------------------------------
% 		Software Developer
\newcommand\ibmSdDescription{Technical delivery lead for client integrations which has included the ordering, installation, and configuration of required hardware, including VPN devices to support client integrations.}

% ----------------------------------------------------------
% 		Data Scientist
\newcommand\ibmDsDescription{Data Ingestions, pre-analytic enrichments, analytic augmentation, data governance, and implementation of assigned client integrations.}

% ----------------------------------------------------------
% 		Data Scientist Consultant
\newcommand\ibmDscDescription{Identified clinical, financial, and operational data elements within different health provider systems to develop data transformations and providing meaning to the data.}

% ----------------------------------------------------------
% AmTrust
% ----------------------------------------------------------
% 		Software Engineer
\newcommand\amtrustDescription{Created multi-tier MVC components and web forms for commercial insurance policy generating software.}

% ----------------------------------------------------------
% PPG
% ----------------------------------------------------------
% 		Color Scientist
\newcommand\ppgDescription{Developed radiative transfer models, spectroscopic profile analysis, and cross-instrument correlation software.}

% ----------------------------------------------------------
% University of Cincinnati
% ----------------------------------------------------------
% 		Research Assistant
\newcommand\ucrDescription{Gathered data in the short-wavelength, crossdispersed mode SXD on a 0.8–5.4 μm spectrograph at NASA IRTF.}

% ----------------------------------------------------------
% Volunteer
% ----------------------------------------------------------
% 		CSforAll
\newcommand\csDescription{Our goal was to provide computer science instruction in all of the District's high schools, with a special emphasis on students who do not have access to a computer or a stable Internet connection at home.}	
% ----------------------------------------------------------
% 		HIT in the CLE
\newcommand\hitDescription{Teams of five students work together to solve a challenge using a large data collection. The purpose is to educate students understand the potential of a career in health information technology and to assist IT companies in Northeast Ohio in developing a talent pipeline.}
% ----------------------------------------------------------
% 		Code for America
\newcommand\cfaDescription{As IT technology evolves, the number and quality of data available to planners and managers changes. The initiative was brought about to apply data science tools to improve and expand public record access.}
% ----------------------------------------------------------
% 		T.C.P. World Academy
\newcommand\tcpDescription{Our goal was to teach students how to understand the value of their learning experience and how to engage in a global society.  Students at T.C.P. World Academy become academically involved and independent learners by participating in society simulation activities for higher learning.}

% ----------------------------------------------------------
% Awards
% ----------------------------------------------------------
%		Gold Champion
\newcommand\gcDescription{For 1,477 classroom hours and earning 43 digital credentials}		
% ----------------------------------------------------------
%		Lab Services Award
\newcommand\lsaDescription{For coordinating internal teams to deliver on time}
% ----------------------------------------------------------
%		Eminence and Excellence Award
\newcommand\eeaDescription{For developing a new data curation tool}
% ----------------------------------------------------------
%		Color Lab Automation Award
\newcommand\claDescription{For expanding data collection and analysis reports}


% ----------------------------------------------------------
% Publications
% ----------------------------------------------------------
%	AI Hackathon 2020
\newcommand\hackDescription{A unique algorithm was designed to accurately anticipate surgery duration using a three-stage process that first uses previous utilization data and current waiting list information to manage case mix distribution.}
% ----------------------------------------------------------
%	REACH - WCI
\newcommand\wciDescription{Analysis of longitudinal patient records and real-time data points through HL7 feeds to provide insights into the patient’s data, and address challenges by integrating within the physician's workflow in the EHR system.}
% ----------------------------------------------------------
%	CDA Learning
\newcommand\cdaDescription{Introduction of implementation of machine learning algorithms using real-world health data analytics.}
% ----------------------------------------------------------
%	IRI Invitational
\newcommand\lakeDescription{Cognitive computing using NLP to extract insights from the unstructured data that holds most of the relevant information and the necessary transformation at the earliest stages of the data integration pipeline.}
% ----------------------------------------------------------
%	METL Training
\newcommand\metlDescription{Seven part series in data ingestion approach using the Hadoop software framework.  Data can be aggregated much more quickly and cost-effectively using a data lake framework than in traditional data warehouses.}


% ----------------------------------------------------------
% Publications
% ----------------------------------------------------------
%	Surgical Scheduling
\newcommand\surgDescription{Improvement on traditional fixed ratio methods for total procedure time estimation, using linear regression models based on relevant variables.}
% ----------------------------------------------------------
%	CCD Integration
\newcommand\ccdDescription{Technical white paper on processes and requirements, overcoming the many difficulties with flat file data curation of CCDs.}
% ----------------------------------------------------------
%	Color Matching
\newcommand\colorDescription{Naive bayesian color and effects matching algorithm for the formula of complex automotive paint formula.}
% ----------------------------------------------------------
%	Chandrasekhar
\newcommand\chandraDescription{Approximation of Chandrasekhar radiative transfer model for atmospheric scattering is applied to color matching.}
% ----------------------------------------------------------
%	Master's Thesis
\newcommand\thesisDescription{Using spectroscopic and photometric analysis of two open clusters to determine the structure of the plane of the Milky Way Galaxy.}
% ----------------------------------------------------------
%	Grad Research
\newcommand\gradrDescription{New near-infrared classification spectra for nine candidate members and comparative 2MASS photometry for several cluster members.}
% ----------------------------------------------------------
%	Undergrad Research
\newcommand\ugradrDescription{Aquatint etching techniques, which have long been employed in intaglio printmaking, may be applied to a novel method for photo-etch procedures.}
