%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Provider Analtyics}
    {Data Scientist} % Data Scientist
    {Merative}
    {Jul. 2022 - Present}
    {
      \begin{cvcompactparagraph}
        Leads end to end delivery of, large \& complex AI and Cognitive led transformation programs and works with Merative and Partners to bring the best tools and delivery methods.  Identify, analyze, and extract key data from heterogeneous systems; and lead technical requirements gathering, data discovery, documentation, and implementation of assigned client integrations.  Manages client resources and drive technical solutions to timely completion.  Works closely with the delivery teams to develop Cognitive, Automation \& AI led programs.  Lead the technical delivery of assigned client integrations which has included the ordering, installation, and configuration of required hardware, including VPN devices to support client integrations.  Configuration and development of software necessary to support client integrations, including ETL and Data Validation.
        % Continuously engages with key clients to effectively communicate value proposition on analytics led insights and embed AI solution in client processes.
      \end{cvcompactparagraph}
    }

%---------------------------------------------------------
  \cventry
    {Watson Health} % Watson Health
    {Advisory Data Scientist}
    {IBM}
    {Nov. 2020 - Jul. 2022}
    {
      \begin{cvparagraph}
        Lead member of Provider Analytics for data integration of disparate and centralized data into data marts, data mining, statistical model development, advanced analytic methods.  Worked closely with senior leaders and colleagues to identify opportunities, set objectives, and formulate analytic strategies that result in measurable impact.  Technical lead on diverse data sources, such as electronic health record data, insurance claims data, scheduling and financial data, social determinants of health data, and any other relevant sources.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {HDP Data Migration}
        \item {Explorys Decomm}
        \item {GP Support for CCF}
        \item {Jira Migration Validation}
        \item {GP Migration}
        \item {DS Certification REACH}
        \item {Surgical Optimization development}
        \item {IHM Validation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Watson Health} % Watson Health
    {Senior Curation Data Architect} % Senior Curation Data Architect
    {IBM}
    {May. 2020 - Nov. 2020}
    {
      \begin{cvparagraph}
        Senior member of Data Onboarding \& Governance for integration of healthcare data and enrichment of metadata. Configuration of data models, analytics, reports, and visualizations. SME to project data architects, delivery, analytics, integration, etc. Directed the configuration of the data onboarding platform and associated infrastructure, and developed improvements to advance stakeholder’s business priorities using tailored analytics.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led cross-function technical team as clinical data analyst for 2020/2021 measure updates project}
        \item {Created machine learning Covid-19 tool that reduced need for hospitalization identification time by up to two weeks}
        \item {Created AI Surgical Scheduling Optimization tool currently evolving into new offering}
        \item {Developed large clinical data integration in excess of several 100 billion structured and semi-structured records for life sciences analytics projects}
        \item {Led HIPAA patient deidentification project from more than 100 data sources for content analytics and measures}
        \item {Served in an advisory capacity for new data platform development project}
        \item {Closed documentation gaps, organizing more than 100 past projects}
        % \item {Placed in the top 6\% of all learners at IBM by completing 285 learning hours in 2020, and earning 8 badges in that time}
        % \item {Awarded band promotion}
      \end{cvitems}
    }

%-----------------------------------------
  \cventry
    {Watson Health} % Watson Health
    {AI Data Curation Architect} % AI Data Curation Architect
    {IBM}
    {Jan. 2018 - May. 2020}
    {
      \begin{cvparagraph}
        Lead member of Data Onboarding \& Governance, member of the Watson Foundation for Health Solutions Architecture team.  Remediation of data issues during UAT.  Built the data onboarding platform and associated infrastructure, and developed improvements to reducing customer implementation cycle time and data triage activities.  Reported on the “health of the data” during data onboarding.  Tuned machine learning classificiation algorithms for patient matching, and led the internal review of similar work by my peers.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % needs 2019 accomplishments
        \item {Reduced mapping rework by 45\% with through new knowledge-driven initiatives}
        \item {Developed new data validation and review process that reduced total rework by 25\%}
        \item {Managed and developed ambitious multi-org enterprise with over 70 interconnected, project-sized components}
        \item {Earned AI certification to peer review tuning algorithm and reviewed over 50\% of projects}
        \item {Curated 25 pages of AI workflow documentation and mentored new hires in AI tuning process}
        \item {Reduced time spent on knowledge transfer by \approx80\% by reorganizing project documentation}
        \item {Spearheaded new-hire mentoring program that led to \approx4,500 increase in total billable hours}
        \item {Awarded Lab Services Award for coordinating internal project teams to deliver client needs on time}
        % \item {Earned 7 badges during IBM Re-skilling Initiative and logged over 200 hours of training in 2018}
        % \item {Awarded GDP bonus for improving revenue per SaaS client by at least 1.34\%}
        % \item {Trained 60\% of current data curation teams, including multiple managers}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {EPM Application Suite} % EPM Application Suite
    {Data Scientist}
    {Explorys, an IBM Company}
    {Jun. 2015 - May. 2018}
    {
      \begin{cvparagraph}
        Data Ingestions, pre-analytic enrichments, analytic augmentation, and data governance.  Identified and extracted key data from multiple heterogeneous systems; and led technical requirements gathering, data discovery, documentation, and implementation of assigned client integrations.  Ordered and oversaw installation of \& configuration of required hardware, including VPN devices to support client integrations.  Configuration and development of software necessary to support client integrations.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Principal integration specialist on over 60 projects for 20 different clients}
        \item {Eliminated need for a \$30,000 annual contract by developing data curation tool}
        \item {Chosen as team lead for \approx12 remote data science contractors for 36 integration projects throughout 2015 - 2017}
        \item {Created over 125 new knowledge base articles, making up 30\% of the team's online content}
        \item {Eliminated average of 3 weeks from employee onboarding process}
        \item {Reduced cost-per-hire by \$5,210 by re-developing education program}
        \item {Awarded Eminence and Excellence Award in 2017 for analytics project}
        % \item {Awarded GDP bonus for improving revenue per SaaS client by at least 1.17\%}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Commercial Package Policies}
    {Software Engineer} % Software Engineer
    {AmTrust Financial Services}
    {Mar. 2014 - Jun. 2015}
    {
      \begin{cvparagraph}
        Developed web forms for insurance industry using ISO standards and created multi-tier MVC components, Web APIs, and UIs using VB, ASP, Javascript, \& HTML5
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development on two software architecture projects in 2015 and principal developer on offering product in 2014}
        \item {Developed over 65 ISO rating based web forms for insurance industry}
        % \item {Collaborated with developers and business analysts to prioritize needs}
        \item {Steered development group into a unit testing project on multi-tier MVC components in 2014}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Automotive Refinish} % Automotive Refinish
    {Color Scientist} % Color Scientist
    {PPG} % PPG Industries
    {Apr. 2012 - Jun. 2013}
    {
      \begin{cvparagraph}
        Developed software and radiative transfer models on complex paint mixtures to determine formulation methods and for spectroscopic profile analysis on color match samples.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved color matching classification algorithm performance by 40\% through new numerical methods}
        \item {Developed cross-instrument correlation software for risk analysis project}
        \item {Awarded Color Lab Automation Award in 2012 for expanding data collection, analyzing automotive pigments and applicable color formulation}
        % \item {Wrote and filed application for patent on the application of the Radiative Transfer Equation (Chandrasekhar) to automotive coatings classification models}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lorain County Community College, Miami University, Cincinnati State Technical and Community College} % Business Unit
    {Adjunct Professor} % Job Title
    {various colleges} % Organization
    {Aug. 2010 - May. 2019} % Date(s)
    {
      \begin{cvparagraph}
        Developed curricula in introductory physics \& astronomy courses, and technical presentations of complex physical concepts for major, non-major, and remedial students.  Wrote concise laboratory instruction manuals, trained in precise measurement techniques \& data analysis using DataStudio, and coordinated analysis documentation.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Exceeded feedback evaluation goals by an average of 16\% in 2017 and by 17\% in 2018}
        \item {Tracked a 28\% reduction in student confusion by reorganizing online education materials}
        \item {Uploaded over 700 hours of lecture material for convenient consumption}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Department of Physics}
    {Research Assistant} % Research Assistant
    {University of Cincinnati}
    {Sep. 2006 - Sep. 2010}
    {
      \begin{cvparagraph}
        Gathered data using SpeX, a 0.8–5.4 μm spectrograph, at the NASA Infrared Telescope Facility.  Observations in the short-wavelength, crossdispersed mode SXD.  Multiple analysis projects comparing 2MASS with measured data, statistical classification without independent photometry for cluster properties, and photometric analysis bootstrapped to independent measurements.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Volunteered 120 hours of Quality Control for the Cambridge Astronomical Survey Unit Variable Stars database}
        \item {Published 3 scholarly articles on near-infrared astrophysics over a 24-month period}
        \item {Awarded Mary J. Hanna Research Fellowship in 2010}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
