%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Trainer} % Role
    {IBM Watson Care Insights Reach Initiative} % Event
    {Watson Health} % Organizing Institution
    {Apr. - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Watson Care Insights aims to analyze longitudinal patient records and real-time data points through HL7 feeds to provide practitioners insights into the patient’s data, and address these challenges by integrating within the physician's workflow in the electronic health record system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Peer Presenter} % Role
    {Content \& Data Analytics Learning Exchange} % Event
    {Watson Health} % Organizing Institution
    {Apr. \& May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduction of implementation of machine learning algorithms and their applications using real-world health data analytics examples.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presenter for the Information Services/Information Technology Network Talks} % Role
    {2018 IRI Fall Networks Conference} % Event
    {Innovation Research Interchange} % Organizing Institution
    {Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
%        \item {Cognitive solutions for closing the gaps on flat file curation}
        \item {Cognitive computing can use NLP to extract insights from the unstructured data that holds most of the relevant information, but also it can also perform the necessary transformation accurately at the earliest stages of the data integration pipeline.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Presenter for the METL Group} % Role
    {Cross Team Training Series} % Event
    {Explorys} % Organizing Institution
    {Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
%        \item {Ingestion using a Data Lake Framework}
        \item {Seven part series in data ingestion approach using the Hadoop software framework.  Data can be aggregated much more quickly and cost-effectively using a data lake framework than in traditional data warehouses, because of the speed and low-cost of massively parallel computing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
