%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Writing}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Technical Development Team - total procedure time estimation} % Role
    {Surgical scheduling optimization and procedure duration prediction} % Title
    {IBM} % Publisher
    {Dec. 2020} % Date
    {
      \begin{cvitems} % Abstract
        \item {Improvement on traditional fixed ratio methods for total procedure time estimation, using linear regression models based on relevant variables.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Integration Developer} % Role
    {Process and Requirements for CCD Data Integration} % Title
    {IBM} % Publisher
    {Oct. 2017} % Date
    {
      \begin{cvitems} % Abstract
        \item {Technical paper on processes and requirements, overcoming the many difficulties with flat file data curation of CCDs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Radiative Transfer Physics} % Role
    {Characterization of Surface Coatings using Radiative Transfer Models for Color Matching} % Title
    {PPG} % Publisher
    {Dec. 2010} % Date
    {
      \begin{cvitems} % Abstract
        \item {Approximation of Chandrasekhar radiative transfer model for atmospheric scattering is applied to color matching.  (U.S Patent Application)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Researcher} % Role
    {Massive Stellar Clusters in the Disk of the Milky Way Galaxy} % Title
    {OhioLINK ETD} % Publisher
    {Dec. 2010} % Date
    {
      \begin{cvitems} % Abstract
        \item {Using spectroscopic and photometric analysis of two open clusters to determine the structure of the plane of the Milky Way Galaxy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Role
    {Near-Infrared Spectroscopy of Candidates Members of the Galactic Cluster [BDS2003] 107} % Title
    {PASP} % Publisher
    {Feb. 2008} % Date
    {
      \begin{cvitems} % Abstract
        \item {New near-infrared classification spectra for nine candidate members and comparative 2MASS photometry for several cluster members.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
